Title Goes Here

### 2021-04-09 analysis/paper/shceof.Rmd
Agrega más barras de colores
(#30)

```{r eof-naive, fig.cap = "(ref:eof-naive-cap)", fig.width=2.5, fig.height=3}
eof_naive[, eof[[1]]$right, by = lev] %>%
  .[lev == 50] %>% 
  periodic(lon = c(0, 360)) %>%
  ggplot(aes(lon, lat)) +
  geom_contour_fill(aes(z = hgt, fill = ..level..),
                    breaks = AnchorBreaks(0, 0.01, exclude = 0)) +
  geom_contour_tanaka(aes(z = hgt), breaks = AnchorBreaks(0, 0.01, exclude = 0), 
                    range = c(0.01, 0.2)) +

  geom_qmap(~.x[lat <= -20], size = 0.1) +
  scale_fill_divergent_discretised(guide = "none")  +
  scale_y_latitude() +
  scale_x_longitude() +
  coord_polar() +
  theme(axis.text = element_blank()) +
  facet_wrap(.~cEOF, ncol = 2, labeller = labeller(lev = lab_lev))  +
  tagger::tag_facets("rc")  +
  theme(panel.spacing = grid::unit(-.7, "lines"))
```

>>>>

```{r eof-naive, fig.cap = "(ref:eof-naive-cap)", fig.width=2.5, fig.height=3.2}
eof_naive[, eof[[1]]$right, by = lev] %>%
  .[lev == 50] %>% 
  .[ , hgt := hgt/sd(hgt)] %>% 
  periodic(lon = c(0, 360)) %>%
  ggplot(aes(lon, lat)) +
  geom_contour_fill(aes(z = hgt, fill = ..level..),
                    breaks = AnchorBreaks(0, 1, exclude = 0)) +
  geom_contour_tanaka(aes(z = hgt), breaks = AnchorBreaks(0, 1, exclude = 0), 
                    range = c(0.01, 0.2)) +

  geom_qmap(~.x[lat <= -20], size = 0.1) +
  scale_fill_divergent_discretised(NULL, guide = guide_colorsteps_bottom(10))  +
  scale_y_latitude() +
  scale_x_longitude() +
  coord_polar() +
  theme(axis.text = element_blank()) +
  facet_wrap(.~cEOF, ncol = 2, labeller = labeller(lev = lab_lev))  +
  tagger::tag_facets("rc")  +
  theme(panel.spacing = grid::unit(-.7, "lines"))
```
